Methods and Results

### 2022-10-03 ms.Rmd
Add in a Geary's test check that data for logCVR/VR are behaving as assumed

>>>>

## Geary's test to check normality assumptions
data <- data %>% 
         mutate(geary_control = geary(X_C, sd_C, N_C),
                    geary_trt = geary(X_T, sd_T, N_T),
                   geary_test = ifelse(geary_control >= 3 & geary_trt >= 3, "pass", "fail"))
# How many fail?
    geary_res <- data %>% group_by(geary_test) %>% summarise(n = n()) %>%  data.frame()
